---
title: "Demonstrate imputeTestbench on a naturally occurring time series."
author: "Arush Banerjee"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Reference: https://cran.r-project.org/web/packages/imputeTestbench/imputeTestbench.pdf


## 1. Choice of Dataset
 I have chosen DAX(German Stock Market Index) from the EuStockMarkets dataset for this test.

The EuStockMarkets dataset is a matrix containing the DAX (Germany), SMI (Switzerland), CAC (France), and FTSE (UK) containing data from January 1, 1991, to February 16, 1998.

I chose this dataset as it satisfies the requirements of the easy test (univariate by choosing the DAX), and in the future can also be used for multivariate imputation. 

This dataset has **high sampling frequency** and is **stochastic in the short term and compounding in the long term** unlike datasets on seasonal data like temp making it ideal for our use case.




## 2. Importing and Plotting the Original Data

```{r}

library(imputeTestbench)


data("EuStockMarkets")
dax_ts <- EuStockMarkets[, "DAX"]  #taking the dax time series from the dataset

plot(dax_ts, 
     main= "Original DAX Time Series", 
     xlab="Year",
     ylab="Index Value(in Deutsche Mark)",
     col="green")

```


This graph is **approximately of exponential type** showing the continued growth of German stock market in these years but also the economic crisis such as of 1997.




## 3. Demonstrating the imputeTestbench package


We will apply three different methods of imputation ("na_mean", "na_interpolation" and "na.locf") on the dataset and compare their accuracy.

```{r}
results <- impute_errors(
  dataIn= dax_ts,
  methods = c("na_interpolation", "na.locf", "na_mean"),
  errorParameter = "rmse", #Gives Root Mean Square Error
  missPercentFrom = 10,
  missPercentTo = 90, 
  interval = 10, #Taking Miss Percent from 10 to 90 at an interval of 10 
  repetition = 10
)

print(results)
```


## 4. Plotting the  errors of different methods


```{r}
plot_errors(results, plotType = 'bar')
```


## 5. Plotting the imputations of different methods at 50% missing data

```{r}
plot_impute(dataIn = dax_ts,
            methods= c("na_interpolation", "na.locf", "na_mean"),
            missPercent = 50,
            showmiss = TRUE
)
```


## 6. Observations from the Plots of errors

**Mean Imputation** consistently has the **highest error** because it ignores the time-dependent nature of stock prices.

**LOCF and Interpolation** perform similarly on this dataset, but as missingness increases, the gaps become wider, and **Linear Interpolation outperformed LOCF** because it utilizes the future's information as well for the gap. 

In a real-world trading bot, you cannot use interpolation because you don't know tomorrow's price yet. You are forced to use LOCF.

## 7. Future Scope

As the different EU stock markets are highly interrelated, thus a bear market in one index gives a high probability that the other markets will also be bearish.

Thus in the future, this dataset can be used for the multivariate time series implementation of imputeTestbench.